Air Quality Data - PM2.5 Components

### 2021-01-03 code/data-processors/air-data-processor.Rmd
Update air-data-processor.Rmd
Added Cross-walk files

```{r load packages}
library(tidyverse)
library(here)
library(lubridate)
library(naniar) # for replacing -999 with NA
```

@@

```{r load data}
load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\state-region.RDa')
```

@@

aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf("%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting = as.factor(ifelse(Location.Setting == "URBAN AND CENTER CITY",
                                        "URBAN",
                                        as.character(Location.Setting)))
    ) %>% 
  merge(state.region[, c("State", "Region.IV")])

@@

>>>>

```{r load packages}
library(tidyverse)
library(here)
#library(lubridate)
#library(naniar) # for replacing -999 with NA
```

@@

```{r load data}
load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\state-region.RDa')
load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip.RDa')
```

@@

aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf("%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting = as.factor(ifelse(Location.Setting == "URBAN AND CENTER CITY",
                                        "URBAN",
                                        as.character(Location.Setting)))
    ) %>% 
  merge(dt.state.region[, c("State", "Region.IV")])

@@

```{r Zipcodes in x-mile bufferzone of Monitoring Sites}
load(here('data', 'processed', 'comp-1yr.RDa'))

dt.comp <- dt.comp.1yr %>% 
  select(Site.ID, Year, Month) %>% 
  mutate(psuedo = 100)

dt.comp <- dt.comp %>% 
  inner_join(dt.site.zip, by = c("Site.ID", "Year")) %>% 
  arrange(Zip.Code, Year, Dist)

# pick the site with shorter distance
site.dist.shorter <- dt.comp %>% 
  group_by(Zip.Code, Year) %>% 
  filter(Dist == min (Dist)) %>% 
  arrange(Zip.Code, Year)

dt.comp.site.zip.bz6 <- dt.comp %>% 
  filter(Dist <= 6)
dt.comp.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4351
dt.comp.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #286

dt.comp.site.zip.bz12  <- dt.comp %>% 
  filter(Dist <= 12)
dt.comp.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8454
dt.comp.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #331

dt.comp.site.zip.bz24  <- dt.comp %>% 
  filter(Dist <= 24)
dt.comp.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15856
dt.comp.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #344
```

```{r}
save(dt.comp.cms, file = here('data', 'processed', 'comp-cms.RDa'))

```
